Implications of afforestation policies for global markets

### 2024-02-20 paper.Rmd
Update paper.Rmd

Establishing a connection between the standard GTAP model and the GTM model was a two-step process. First, we identified the set of common variables that are included in both models and their closures. That is, we selected which variables would be determined endogenously by one model and held as exogenous for the other model. In our case, we selected the return on land to be modeled by the GTAP model and fed into the GTM model as exogenous, while the amount of land available for crop and livestock production, while exogenous to the GTAP model, is endogenously determined by the GTM model. In the second, step we establish the connection between the models on the software level. This step requires that the GTAP model, written in GEMPACK can operate with the inputs from the GTM model, written in GAMS, and submit the outputs back to the GTM model. In order to allow for the two quite dated technologies, GEMPACK and GAMS, which were developed long time age before software integration become important or possible, we created a set of user functions in R that allow executing both models, collecting their outputs and an creating  parameter files for both systems automatically.

>>>>

Establishing a connection between the standard GTAP model and the GTM model was a two-step process. First, we identified the set of common variables that are included in both models and their closures. That is, we selected which variables would be determined endogenously by one model and held as exogenous in the other model. In our case, we modeled the return on land using the GTAP model and fed those results into the GTM model as exogenous. Then, the amount of land available for crop and livestock production was endogenously determined by the GTM model and fed into the GTAP model as an exogenous input. In the second step, we established the connection between the models on the software level. This step required that the GTAP model, which is written in GEMPACK, be able to handle with the inputs from the GTM model, which is written in GAMS, and submit the outputs back to the GTM model. As GEMPACK and GAMS were developed long before software integration became important or even possible, we had to create a set of user functions in R that executed both models, collected their outputs, and an created parameter files automatically.
